---
title: "Untitled"
author: Me
date: 2025-10-09
format: html
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(here)
interviews <- read_csv(here("data/SAFI_clean.csv"), na = "NULL")
```


# My title
## Section
### Subsection
#### Subsubsection

## Introduction

This report uses the *tidyverse* (meta)***package*** along with the **SAFI** data set,  
which has columns that include:

- village
- interview_date
- no_membrs
- years_liv
- respondent_wall_type

These are my favourite variables:

1. no_meals
1. interview_date
2. no_membrs
3. village

A nested list:

- village
  + Name of village
- interview_date
  + Date of interview
- no_membrs
  * Number of members in the household
- years_liv
- respondent_wall_type

## Materials and Methods

```{r}
#| label: tbl-random-table
#| tbl-cap: "Some random table with some random numbers."
#| echo: false
#| message: false
interviews %>% 
  filter(!is.na(memb_assoc)) %>% 
  group_by(village, memb_assoc) %>% 
  summarise(mean_no_members = mean(no_membrs)) %>% 
knitr::kable(
col.names = c("Village", "Member Association", "Mean number of members")
)
```




